### 2023-06-23 vesicle_code/docs/confinedMulti/multicomponent_vesicles.tex
updated Fig 15

\begin{figure}[H]
    \centering
    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(a)}{figures/Fig14f.pdf}
    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(b)}{figures/Fig14a_newPaper.pdf}
    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(c)}{figures/Fig14b_newPaper.pdf}
    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(d)}{figures/Fig14c_newPaper.pdf}
    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(e)}{figures/Fig14e_newPaper.pdf}
  \caption{\label{fig:RA5} \small A vesicle passing through a
  contracting geometry. The vesicle's reduced area is $\alpha = 0.5$ and
  the dimensionless maximum velocity is $Ca = 0.25$. The vesicles are:
  (a) single-component with bending modulus $b=1$; (b) multicomponent
  with 15\% floppy region; (c) multicomponent with 25\% floppy region;
  (d) multicomponent with 35\% floppy region; (e) multicomponent with
  45\% floppy region. The vesicles with a larger percentage of floppy
  regions pass through the neck earlier than the vesicles with less
  percentage of floppy regions.}
\end{figure}

>>>>

\begin{figure}[H]
  \centering
  \includegraphics[width=\columnwidth]{figures/Contracting_RAp6MC_variableConc.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(a)}{figures/Fig14f.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(b)}{figures/Fig14a_newPaper.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(c)}{figures/Fig14b_newPaper.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(d)}{figures/Fig14c_newPaper.pdf}
%    \subfigimg[width=\columnwidth,trim ={5cm .5cm 1.5cm .5cm},clip]{(e)}{figures/Fig14e_newPaper.pdf}
  \caption{\label{fig:RA5} \small A vesicle passing through a
  contracting geometry. The vesicle's reduced area is $\alpha = 0.5$ and
  the dimensionless maximum velocity is $Ca = 0.25$. The vesicles are:
  (a) single-component with bending modulus $b=1$; (b) multicomponent
  with 15\% floppy region; (c) multicomponent with 25\% floppy region;
  (d) multicomponent with 35\% floppy region; (e) multicomponent with
  45\% floppy region. The vesicles with a larger percentage of floppy
  regions pass through the neck earlier than the vesicles with less
  percentage of floppy regions.}
\end{figure}
